Boosted Regression Trees for Data-Driven Auto-Tuning

### 2011-12-09 paper/draft1.tex
paper

This work shows that online auto-tuning can be accelerated by orders of
magnitude by using a regression model built offline as a surrogate for actual
computations on the real hardware.
We use a powerful non-linear regression model (boosted decision trees)
to approximate the empirical relationship between three sets of variables ($\mathcal{A},
\mathcal{B}, \mathcal{C}$) and the observed speed-up over a
reference implementation:
\begin{description}
\item[$\mathcal{A}$:] task description (e.g. shapes, physical layout)
\item[$\mathcal{B}$:] algorithm description (i.e. auto-tuning parameters)
\item[$\mathcal{C}$:] platform description (e.g. micro-benchmarks)
\end{description}
Ideally, \texttt{gpu\_fbcorr} would apply the best
available implementation

@@

@@

On the GTX 295, a single decision-tree fit to the log-speed-multiplier
(LSM) function (XXX: how many problem configurations, how much vs. what
kind of training data) achieves an average Spearman correlation of 0.9 on
held-out test data (XXX: what kind of test data).

>>>>

This work shows that online auto-tuning can be accelerated by orders of
magnitude by using a regression model built offline as a surrogate for actual
computations on the real hardware.
We use a powerful non-linear regression model (boosted regression trees)
to approximate the empirical relationship between three sets of variables ($\mathcal{A},
\mathcal{B}, \mathcal{C}$) and the observed speed-up over a
reference implementation:
\begin{description}
\item[$\mathcal{A}$:] task description (e.g. shapes, physical layout)
\item[$\mathcal{B}$:] algorithm description (i.e. auto-tuning parameters)
\item[$\mathcal{C}$:] platform description (e.g. micro-benchmarks)
\end{description}
Ideally, \texttt{gpu\_fbcorr} would apply the best
available implementation

@@

\section{Boosted Regression Trees}

The regression tree is a piece-wise constant function

Boosted regression trees are

@@

On the GTX 295, a single regression-tree fit to the log-speed-multiplier
(LSM) function (XXX: how many problem configurations, how much vs. what
kind of training data) achieves an average Spearman correlation of 0.9 on
held-out test data (XXX: what kind of test data).
